Twisted 11-dimensional supergravity

### 2021-10-14 intro.tex
stuff

In this paper, we provide perturbative descriptions of all twists of eleven-dimensional supergravity. 
%By `twists' we mean ones which arise from setting a bosonic ghost to take a nonzero value of a particular supertranslation in the 11-dimensional supersymmetry algebra. 
Thanks to a straightforward classification, which we recall below, there are essentially two types of twists which deform the flat background $\RR^{11}$: 
\begin{itemize}
\item The minimal (or holomorphic) twist. 
The resulting twisted theory is defined on $\CC^5 \times \RR$ and is holomorphic along $\CC^5$ and topological along the `time' direction~$\RR$. 
The twist is $SU(5)$ invariant and involves a fixed choice of a Calabi--Yau form on $\CC^5$. 
\item The non minimal twist. 
The resulting twisted theory is defined on $\CC^2 \times \RR^7$ and is holomorphic along $\CC^2$ and topological along $\RR^7$.
The twist is $SU(2)$ invariant and involves a fixed choice of a hyper K\"ahler structure on $\CC^2$.  
\end{itemize}

In \cite{SWspinor}, the last two authors used the formalism of pure spinors to describe the {\em free field limit} of the minimal twist of 11-dimensional supergravity on flat space.
\brian{also reference fabian and richard}
The resulting theory is $\ZZ/2$ graded which is inherited from the ghost grading and parity in the original, untwisted, 11-dimensional theory.
In \S\ref{sec:dfn} we extend this free limit of the twist of 11-dimensional supergravity to a fully interacting theory in the Batalin--Vilkovisky (BV) formalism.\footnote{One subtlety is that unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the 11-dimensional theory is only $\ZZ/2$ graded.
All odd fields can therefore be considered as ``ghosts'' in the twisted theory.}
Our main conjecture is that this interacting BV theory is equivalent to the minimal twist of 11-dimensional supergravity on flat space.

>>>>

In this paper, we provide perturbative descriptions of all twists of eleven-dimensional supergravity. 
%By `twists' we mean ones which arise from setting a bosonic ghost to take a nonzero value of a particular supertranslation in the 11-dimensional supersymmetry algebra. 
Thanks to a straightforward classification, which we recall below, there are essentially two types of twists which deform the flat background $\RR^{11}$: 
\begin{itemize}
\item The minimal (or holomorphic) twist. 
The resulting twisted theory is defined on $\CC^5 \times \RR$ and is holomorphic along $\CC^5$ and topological along the `time' direction~$\RR$. 
The twist is $SU(5)$ invariant and involves a fixed choice of a Calabi--Yau form on $\CC^5$. 
\item The non-minimal twist. 
The resulting twisted theory is defined on $\CC^2 \times \RR^7$ and is holomorphic along $\CC^2$ and topological along $\RR^7$.
The twist is $SU(2)$ invariant and involves a fixed choice of a hyper K\"ahler structure on $\CC^2$.  
\end{itemize}

In~\cite{SWspinor}, the last two authors used the pure spinor formalism to describe the {\em free field limit} of the minimal twist of 11-dimensional supergravity on flat space, following work of Cederwall~\cite{Ced-towards,Ced-11d}. In fact, the result of that paper shows that the pure spinor formalism is compatible with twisting, so that the twist of any multiplet can be recovered from the algebraic geometry of a neighborhood of the corresponding point in the scheme of square-zero elements.
(In separate work~\cite{EagerHahner}, the free-field limit of the non-minimal twist was derived from the component-field multiplet as used in the physics literature.)
%\brian{also reference fabian and richard}
The resulting theory is $\ZZ/2$ graded; the grading is inherited from the totalization of ghost number and intrinsic parity in the original, untwisted, eleven-dimensional theory.
In \S\ref{sec:dfn} we extend this free limit of the twist of 11-dimensional supergravity to a fully interacting theory in the Batalin--Vilkovisky (BV) formalism.\footnote{One subtlety is that unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the 11-dimensional theory is only $\ZZ/2$ graded.
All odd fields can therefore be considered as ``ghosts'' in the twisted theory.}
Our main conjecture is that this interacting BV theory is equivalent to the minimal twist of 11-dimensional supergravity on flat space.
